---
title: "Quarto Presentations"
format: 
  html:
    code-link: true
date: today
date-format: "D. M. YYYY"
---

## General

STAYING UP TO DATE: QUARTO NEWS on download page release notes

`ctrl + space` to see yaml or hashpipe (#|) options.


### Report date

[Documentation](https://quarto.org/docs/reference/dates.html)

```
---
date: today
date-format: "D. M. YYYY"
---
```

## Parameters

### Python

Python runs on the `reticulate` package.

Jupyter engine uses [Papermill](https://github.com/nteract/papermill) style parameters meaning that the cell is tagged "parameters".
Parameters are first class objects - In the example below we can access `alpha` as an object in python.

```
#! tags: [parameters]

alpha=0.1
beta=0.1
```


### R

YAML - Yet Another Markup Language

`knitr` engine - Assign values in YAML. Parameters are then saved in a list called `params`
---
params:
  alpha: 0.1
  beta: 0.1
---

They can be accessed with:

- `params$alpha`
- `params$beta`



### Render with parameters:

With the Command Line Interface:

`quarto render report.qmd -P alpha:0.2 -P beta:0.2 --output report.html`

Note: Parameters must be set in the document before passing them to the render command.

`quarto render report.qmd --to html`
`quarto render report.qmd --to pdf`


## Including files

We can also include custom CSS, JavaScript, Html files. [See here](https://quarto.org/docs/reference/formats/html.html#includes)

Example:

| denotes that the value is a multi-line string.

```
---
include-in-header: 
  - text: |
    <style> class {color: red;} </style>
    <link rel = "stylesheet" href = "..."/>
  - file: main.js
  - style.css
---
```


## Unified syntax

Unified syntax for multiple output formats. Using pandoc syntax allows to easily convert to different formats. That is one reason to prefer the use of **:::** to denote blocks over the html <div> syntax.

[Markdown basics](https://quarto.org/docs/authoring/markdown-basics.html)

### Pandoc fenced divs

Starts and ends with equal number of : (at least 3).

Example:

Class is used to style the block inside. The block's id is set to `id`.

```
::: {#id class}

Block to modify with class

:::
```




### Bracketed spans

Inline styling. 
  
`[This is *some text*]{.class key="val"}˙`

[This is *some text*]{.class key="val"}


### Footnotes

`This is some text^[This is a footnote]`

This is some text^[This is a footnote]

in format html: citations-hover:true
in format html: footnotes-hover:true

### Other predefined attributes

.panel-tabset (HTML ONLY)
.fragment (REVEALJS ONLY)


### Figures, Layouts 

[Link](https://quarto.org/docs/authoring/figures.html)

- `layout-ncol=2`
- `layout-nrow=2`
- `layout="[[30,70], [100]]"` (two rows, first row 2 divs with flex-basis 30-70 and second row with one div with 100 flex basis)

Below is an example using `:::{layout-ncol=2}` .

::: {#id layout-ncol=2}
left col

right col
:::


And of using `:::{layout="[[30,70], [100]]"}` .

::: {layout="[[30,70], [100]]"}
top row-left col

top row-right col

Bottom row
:::


## Code

- Hide code:

```
---
execute:
  echo: false
---
```

  
- Fold code:

```
---
html:
  code-fold:true
  code-summary:"text"
---
```

Or using hashpipe inside a specific chunk:

```
#| code-fold: true
#| code-summary: "View source code"
#| fig-align: "center"

plot(1:50, 1:50)
```

```{r}
#| code-fold: true
#| code-summary: "View source code"
#| fig-align: "center"

plot(1:50, 1:50)
```


-Code tools:

```
---
html:
  code-tools: 
    source: true
    toggle: false
    caption: none 
---
```


- Code linking

`downlit` package for linking source code functions to documentation. `#! code-link: true`?

```
---
html:
  code-link: true
---
```


```{r}
x <- 3
y <- 2
z <- x * y
plot(1:50, 1:50)
```


- Code line numbers:

```
#| code-line-numbers: true
x <- 3
y <- 2
z <- x * y
# ....s
```

```{r}
#| code-line-numbers: true
x <- 3
y <- 2
z <- x * y
# ....s
```

## Callout blocks

[Documentation](https://quarto.org/docs/authoring/callouts.html)

```
::: {.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::
```

::: {.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

::: {.callout-tip}
## Tip With Caption

This is an example of a callout with a caption.
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

## Aesthetics

Quarto uses the bootstrap CSS library with 25 themes from bootswatch as default. You can add cusom css, scss, sass files:

```
---
format:
  html:
    theme: [default, custom.scss]
---
```

### Emojis

---
from: markdown+emoji
---



# REAVEALJS

```
---
format:
  revealjs
---
```

## Tips

-Alt+click to zoom in to a section

- alt + + to zoom ?

- Use {.fragment} to incrementally add content

- Show the code first and then show the output as you move 

`#| output-location:column-fragment`

- Use level-2 headers `##` to define slides

## Lists

- Incremental lists

```
:::{.incremental}
-
-
:::
```

- Non-incremental lists

```
:::{.nonincremental}
-
-
:::
```



## Highlight code line number


```
#| code-line-numbers: "1, 3-4"
x <- 3
y <- 2
z <- x * y
# ....s
```

## Layout

### Multiple columns

```
::::{.columns}

:::{.column .fragment}
One Column
:::

:::{.column .fragment}
Another Column
:::
::::
```

::::{.columns}

:::{.column .fragment}
One Column
:::

:::{.column .fragment}
Another Column
:::
::::


### Absolute positioning

Specify ditance from borders (left/right + top/bottom)

```
::: {.absolute top= right= bottom= left=}
:::
```

## Aesthetics

### Themes

[Themes](https://quarto.org/docs/presentations/revealjs/themes.html)

Quarto RevealJS presentations come with 10 built-in themes.

```
---
title: "Title"
format:
  revealjs:
    theme: [beige, custom.scss]
---
```


### Logo
```
format:
  revealjs:
    logo: "logo.png"
```

### Footer

```
format:
  revealjs:
    footer: "Some footer"
```

One-off footer (only displayed on the corresponding slide):

```
:::{footer}
one off
:::
```

### Slide backgrounds

Changing the background colour will change the text color automatically.

- Background color:

`## Slide Background {background-color="black",...}`

- Background images:

`## Slide Background {background-image=".." background-repeat="...",...}`

- Background images:

`## Slide Background {background-video=".." background-repeat="...",...}`


### Stacking content

Stack images on top of each other
```
:::{.r-stack .fragment}
img1

img2

img3
:::
```



